\vspace{-0.25em}\thetitle

### 2009-07-29 paper.tex
...

We use randomly sampled traffic from six different network traces.
All six traces are freely available from the \caps{CRAWDAD} wireless trace repository~\cite{Yeo06}.
These traces represent a cross-section of traffic patterns over time and a reasonable variety of network types.
Unfortunately, we could find no freely available commercial hotspot or corporate network traces that were usable for our analysis.
We randomly sampled 5000 flows from each trace for training and another 5000 flows for testing.

@@

>>>>

We use randomly sampled traffic from six different network traces.
All six traces are freely available from the \caps{CRAWDAD} wireless trace repository~\cite{Yeo06}.
Details of the traces are shown in \Table{traces}.
These traces represent a broad cross-section of traffic patterns over time and a reasonable variety of network types.
Unfortunately, we could not find and freely available commercial hotspot or corporate network traces that were usable for our analysis.
We randomly sampled 5000 flows from each trace for training and another 5000 flows for testing.

@@

Once the data have been expressed in matrix form, the next step is attempt to detect the linear structures seen in \Figure{svd}.
% Recall that these correspond to the point classes in our hypothesized model.
We use Ma~\emph{et~al.}'s~\cite{Ma07} algorithm for segmenting multivariate data into a union of subspaces using lossy data coding and compression.
The essential idea of this algorithm is to compute the number of bits needed to encode the data under various assumed groupings and their implied distributions.
The grouping which leads to the least overall encode size is the desired segmentation.
This algorithm has many desirable qualities:
unlike most clustering algorithms, it finds subspaces, not full-rank regions;
it is highly robust to outliers and noisy data.
This algorithm has one parameter:
the maximum allowable distortion of the data, $\varepsilon^2$.
We follow Ma's lead when applying their algorithm to \caps{SVD} data and use $\varepsilon^2 = 1$.
The result of this stage is a segmentation of the data into classes of rows, precisely as our hypothesized model requires.
